---
title: "README for BestModelAICBIC"
output: github_document
---

1. Find best model among all independent variables based on AIC or BIC values.
2. The underlying model is a simple multiple linear regression.
3. Function to finding AIC and BIC values to identify best model for GLM models is underconstruction.  

```{r cars}
BestModelAICBIC::bm_aic_bic(data = mtcars, depvar = "mpg", crit = "BIC")
```
  
#Prepare dataset for different scenarios

```{r warning=FALSE}
#Curtailed dataset with reduced data and interaction terms
new_df <- dplyr::mutate(mtcars[c("mpg","disp","drat","vs","am")], interaction.term = disp*drat)

#Run model for BIC
BestModelAICBIC::bm_aic_bic(data = new_df, depvar = "mpg", crit = "AIC")
```

```{r warning=FALSE}
#Run model for AIC
BestModelAICBIC::bm_aic_bic(data = new_df, depvar = "mpg", crit = "BIC")
```
Notice that according to the AIC the best model includes: "disp", "drat" and "interaction.term". Whereas the BIC best model only contains: "drat" and "interaction.term". 